Monte Carlo for all parameters

### 2024-07-25 MC_all.Rmd
Failure with local density for now

---
title: "Making sure the variances converge"
output:
  pdf_document: default
  html_document: default
date: "2024-07-12"
---

@@

MonteCarlo <- function(n, B, f){
  # n: sample size; 
  # B: number of iterations for MC; 
  # f: function to consider (with 2 variables, x and y)

  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
  est_MC <- c() # Vector containing all estimations
  for (b in 2:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    # Variable of interest derived from the sample
    a <- mapply(f, a1, a2)
    est_MC <- append(est_MC, sum(a/p))
  }

  return(var(est_MC))
  # Monte-Carlo variance
}
```

>>>>

---
title: "Monte Carlo for all parameters"
output: pdf_document
date: "2024-07-24"
---

@@

MonteCarlo <- function(n, B){
  # n: sample size;
  # B: number of iterations for MC

  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density

  MC_df <- data.frame(useless = rep(0, n))
  MC_est <- data.frame(useless = rep(0, 3), row.names = c("est_nb", "est_vol", "est_ratio"))

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    # Variables of interest derived from the sample
    var_nb <- mapply(circle_nb, a1, a2)
    var_vol <- mapply(circle_vol, a1, a2)
    MC_b <- data.frame(x = a1, y = a2, z = var_nb, t = var_vol)
    MC_df <- cbind(MC_df, MC_b)
    colnames(MC_df)[4*(b-1)+2] <- paste("x", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+1] <- paste("y", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+2] <- paste("nb", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+3] <- paste("vol", b, sep = "")
    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
    MC_est <- cbind(MC_est, est_b)
    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
  }
  MC_df$useless <- NULL
  MC_est$useless <- NULL
  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
  return(list(MC_df, MC_est, MC_var))
}
```

```{r}
# Small test

start.time <- Sys.time()

res_MC <- MonteCarlo(100, 200)
